---
title: "BMS 225a Workshop 2"
author: "Celeste Garza"
date: '2023-10-12'
output:
  pdf_document: default
  html_notebook: default
---

#Weather Data Analysis

```{r load_packages}
library(tidyverse)
```

#head(sf_weather)
```{r Read in data}
sf_weather <- read.csv("../raw_data/sf_weather_2023.csv")

head(sf_weather)
colnames(sf_weather)

select(sf_weather, DATE)

head(Date)

sf_weather_temp <- sf_weather %>%
select(c(DATE, TMAX, TMIN)) %>%
na.omit()

separate(DATE, c("YEAR", "MONTH", "DAY"), sep= "-", remove = FALSE) %>/%
filter(YEAR == "2021") %>%
mutate(TAVG = ( (TMAX + TMIN)/2 ) ) %>%
group_by(MONTH) %>%
summarize (MAX_MO_TEMP) =max(TAVG)
#```{r Subset and split out data}
#sf_weather_temp <- sf-weather %>%
#select(c(DATE, TMAX, TMIN)) %>%
# no.omit()

#separate(DATE, c("YEAR", "MONTH", "DAY"), sep= "-", remove = FALSE) %>/%
#filter(YEAR == "2021") %>%
#mutate(TAVG = ( (TMAX + TMIN)/2 ) ) %>%
#group_by(MOTNTH) %>%
#summarize (MAX_MO_TEMP) =max(TAVG))
```

# ``` {rSubset the data}
#select(af_weather, DATE)

#head(date)

#```{r Subset and split out data}
#sf_weather_temp <- sf-weather %>%
#select(c(DATE, TMAX, TMIN)) %>%
# no.omit()

#separate(DATE, c("YEAR", "MONTH", "DAY"), sep= "-", remove = FALSE) %>/%
#filter(YEAR == "2021") %>%
#mutate(TAVG = ( (TMAX + TMIN)/2 ) ) %>%
#group_by(MOTNTH) %>%
#summarize (MAX_MO_TEMP) =max(TAVG))

```{r Plotting our data}
plot(sf_weather_temp)
```

```{r Apllying functions}
yearly_subsetter <- function(year){}
##```{r Subset and split out data}
#year_subset<- sf-weather %>%
#select(c(DATE, TMAX, TMIN)) %>%
# no.omit()

#separate(DATE, c("YEAR", "MONTH", "DAY"), sep= "-", remove = FALSE) %>/%
#filter(YEAR == "") %>%
#mutate(TAVG = ( (TMAX + TMIN)/2 ) ) %>%
#group_by(MOTNTH) %>%
#summarize (MAX_MO_TEMP) =max(TAVG))

return(year_subset)

#yearly_subsetter("2020")

#```{r Apply function to data}
year_var <- "1980"

yearly_subsetter(year = year_var)
```

#{r Apply function with loops, fig.height=6, fig.width=4}
for {my_year_var in c("1970", "1980", "1990". "2000") ) }
#plyt(yearly_subletter(year = my_year_var), main = my_year_var)
}
```

#summary(sf_weather_temp)
#```



#